---
title: "audit_project"
output: html_document
date: "2023-11-13"
---

### Load Libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggcorrplot)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(caTools)
library(ROSE)
library(e1071)
library(caret)
library(plotROC)
library(psych)
library(rpart)
library(ISLR)
library(DMwR2)
library(performanceEstimation)
library(rpart.plot)
library(Metrics)
library(pROC)
library(corrplot)
```

### Overview

This is a sample of 1 row with headers explanation:

1,PAYMENT,1060.31,C429214117,1089.0,28.69,M1591654462,0.0,0.0,0,0

step - maps a unit of time in the real world. In this case 1 step is 1 hour of time. Total steps 744 (30 days simulation).

type - CASH-IN, CASH-OUT, DEBIT, PAYMENT and TRANSFER.

amount - amount of the transaction in local currency.

nameOrig - customer who started the transaction

oldbalanceOrg - initial balance before the transaction

newbalanceOrig - new balance after the transaction.

nameDest - customer who is the recipient of the transaction

oldbalanceDest - initial balance recipient before the transaction. Note that there is not information for customers that start with M (Merchants).

newbalanceDest - new balance recipient after the transaction. Note that there is not information for customers that start with M (Merchants).

isFraud - This is the transactions made by the fraudulent agents inside the simulation. In this specific dataset the fraudulent behavior of the agents aims to profit by taking control or customers accounts and try to empty the funds by transferring to another account and then cashing out of the system.

isFlaggedFraud - The business model aims to control massive transfers from one account to another and flags illegal attempts. An illegal attempt in this dataset is an attempt to transfer more than 200.000 in a single transaction.

### Read and analyze data

```{r}
# Reading the csv file
fraud_df <- read.csv('credit_card_fraud_data.csv', header = TRUE, na.strings=c(""))

# IsFraud is needs to be converted to factor type
fraud_df$isFraud <- factor(fraud_df$isFraud, levels=c(1,0))

summary(fraud_df)
head(fraud_df)
# Count the total number of records
print(nrow(fraud_df))



```

### Split Test Train

```{r, echo=FALSE}

trainIndex <- createDataPartition(fraud_df$isFraud, p=0.8, list= FALSE)

training_data <- fraud_df[trainIndex, ]
testing_data <- fraud_df[-trainIndex, ]

dim(training_data)
dim(testing_data)
```

### Smote to counter class imbalance

```{r, echo=FALSE}

```

### Logistic Regression

```{r, echo=FALSE}
plot(pressure)
```
